### 2011-05-11 paper.tex

>>>>

\section{Polynomial Time Reductions}

One of the technical details that will arise in many of our results is the need for polynomial time reductions. In this section, we will establish that all $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity classes are closed under polynomial time reductions. In particular, we need.

\begin{prop}
Let $C$ be a $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class and let $T$ be a mapping $\{0,1\}^n \to \{0,1\}^m$ defined by a polynomial time Turing machine. Then if $f \in C$, $f\circ T \in C$.
\end{prop}

This follows from the following four lemmas:

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
\end{proof}
We wish to show that if $f \in \Sigma \cdot C$, then $f \circ T \in \Sigma \cdot C$. We have that 
\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Pi \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\bp \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\parity \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}
